---
title: "LMwithpred"
author: "Kathleen Giba"
date: "11/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
This is the linear model with prediction problem.  
Predict strenght score using data from the following web site.  

```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",
sep="", header=TRUE)  
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require (ggplot)
```
###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)  
```   

In this plot it shows all the different arm ranges among the applicants. 

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))  
```
##Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```  

In this model it shows a straight line to give a better range between Sims and Arms too be able to get the best people to choose from for the job. 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,new,interval="prediction")
```  
###Plot scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))  
```
##Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```  

```{r}
model.2 <- lm(SIMS~GRIP ,data=data)
summary.lm(model.2)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,new,interval="prediction")
``` 
  
```{r}
model.3 <- lm(SIMS~ARM +GRIP  ,data=data)
summary.lm(model.3)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.3,new,interval="prediction")
``` 
```{r}
anova(model.1,model.3)
```

##Conclustion  
The null hypothesis is that there is no difference in the models. Any one of them is as good as the other.  
 We reject the Null Hypothesis,Based on the P Value being less than 0.5, and the R squared showed in Model 1is that Multiple R-squared:  0.4706,	Adjusted R-squared:  0.467 and in Model 3 shows, Multiple R-squared:  0.5422,	Adjusted R-squared:  0.5358, Model 3 is a better predictor than Model 1. 



